% with help from this awesome post
% http://texblog.org/2012/04/25/writing-a-cv-in-latex/

\documentclass[a4paper, 10pt]{article}
\usepackage[margin=3cm]{geometry}
\usepackage{helvet}

\usepackage{hyperref}
\hypersetup{
   colorlinks,
   citecolor=black,
   filecolor=black,
   linkcolor=black,
   urlcolor=blue
}

\usepackage{url}
\usepackage{bibentry}

% Reformat the date
% http://www.howtotex.com/packages/customize-the-date-format-in-your-latex-documents/
\usepackage{datetime}
\newdateformat{mydate}{\THEYEAR\ \monthname[\THEMONTH] \THEDAY}

\title{\bfseries\Huge Dave Ting Pong Tang}
\author{
   \href{mailto:davetingpongtang@gmail.com}{davetingpongtang@gmail.com}
}
\date{\mydate\today}

\usepackage{array, xcolor}
\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\begin{document}

\maketitle

% http://en.wikibooks.org/wiki/LaTeX/Boxes#minipage_and_parbox
\begin{minipage}[ht]{.40\textwidth}\centering
6-5 Ono-cho Tsurumi \\
Yokohama 230-0046 \\
Japan
\end{minipage}
\begin{minipage}[ht]{.50\textwidth}\centering
Twitter: \href{https://twitter.com/davetang31}{@davetang31} \\
GitHub: \href{https://github.com/davetang}{davetang} \\
Blog: \href{http://davetang.org/muse}{http://davetang.org/muse}
\end{minipage}

\section*{Summary}

I entered the field of bioinformatics in 2005 when I started my honours project investigating the extent of lateral gene transfer in \textit{Staphylococcus}. It was then I was introduced to sequence alignment, phylogenetics, and Unix and Perl. Upon completion of my honours degree, I was unsatisfied with my computational skills and invested five months as a work experience trainee in the lab of Brian Dalrymple. I worked closely with Wes Barris, a systems administrator at that time, who was instrumental in helping me improve my Unix and Perl skills. After my work experience I was hired in the same lab to provide bioinformatic assistance to the International Sheep Genomics Consortium and to assist in the annotation of non-coding RNAs for the Bovine Genome Consortium. I next joined the lab of Sean Grimmond as a Laboratory Information Management System developer for the GUDMAP project. I developed \href{http://uqgudmap.imb.uq.edu.au/tools.html}{various tools} and maintained all the data generated by the University of Queensland GUDMAP team.

In 2010, I decided to pursue a PhD degree as a Marie Curie Early Stage Researcher in the lab of Piero Carninci. I worked on analysing high-throughput sequencing data and received training in various aspects of genomics and transcriptomics. I was active as a PhD student and organised the Student Journal Club, the Chat With Guest sessions, and was involved in organising a conference and workshop. I'm passionate about bioinformatics and maintain a \href{http://davetang.org/muse}{blog} where I write about my bioinformatic and research experiences, and provide technical posts to assist people with their bioinformatic analyses.

\section*{Personal}
\begin{tabular}{L!{\VRule}R}
   DOB & 1983 March 31\textsuperscript{st} \\
   Birth place & Hong Kong \\
   Nationality & Australian and British National (Overseas) \\
\end{tabular}

\section*{Education}
\begin{tabular}{L!{\VRule}R}
   2010--2015 & PhD Candidate, Vrije University, the Netherlands. \href{https://github.com/davetang/thesis}{PhD thesis}: High-throughput sequencing and transcriptomics: data analysis and methods development of large expression data sets. \\
   2001--2005 & BSc (Honours) in biochemistry and microbiology, University of Queensland, Australia. \href{https://github.com/davetang/cv/blob/master/honours_thesis.pdf}{Honours thesis}: Using a supertree approach to detect laterally transferred genes within \textit{Staphylococcus}. \\
\end{tabular}

\section*{Past Scientific Positions}
\begin{tabular}{L!{\VRule}R}
   2010--2015 & Research Associate in the lab of Piero Carninci at RIKEN Yokohama, Japan \\
   2008--2010 & Research Assistant in the lab of Sean Grimmond at The University of Queensland, Australia \\
   2006--2008 & Research Assistant in the lab of Brian Dalrymple at the Commonwealth Scientific and Industrial Research Organisation, Australia \\
   2005--2006 & Research Assistant in the lab of Mark Ragan at the University of Queensland, Australia \\
\end{tabular}

\section*{Research Interests}

\begin{itemize}
   \setlength\itemsep{0em}
   \item Genomics and transcriptomics; in particular the study of non-coding RNAs and transposable elements expression.
   \item The application of bioinformatics, in particular machine learning and data mining methods, to biological problems.
   \item Open science and reproducible research.
\end{itemize}

\section*{Bioinformatic Skills}

\begin{itemize}
   \setlength\itemsep{0em}
   \item Data analysis of high-throughput sequencing data from various *Seq protocols.
   \item Knowledge and the ability to use various bioinformatic databases, repositories, and tools.
   \item The application of biostatistics to the analysis of high-throughput sequencing data.
\end{itemize}

\section*{Computer Skills}

\begin{itemize}
   \setlength\itemsep{0em}
   \item Operating systems: Linux/Unix (RHEL/CentOS and Ubuntu), OS X, and Windows.
   \item Programming/scripting languages: Perl, R, SQL, bash, PHP, JavaScript, Python, and C.
   \item Pre Web 2.0: CGI, PHP, HTML, MySQL, Apache2, and JavaScript.
   \item Open science and reproducible research tools: git, GitHub, WordPress, Jekyll, and R Markdown/Markdown.
\end{itemize}

\section*{Honours and Awards}
\begin{tabular}{L!{\VRule}R}
   2010 & CSIRO Chairman's Medal \\
   2008 & CSIRO Partnership Excellence Award \\
\end{tabular}

\section*{Workshop and Course Attendances}
\begin{tabular}{L!{\VRule}R}
   2014 & RIKEN/KI doctoral course: Employing Genome-wide Technologies for Functional Regulation in Development and Disease \\
   2013 & AMATA conference ECR workshop \\
   2013 & Coursera data analysis course from Johns Hopkins University \\
   2013 & BrainTrain \href{http://www.brain-train.nl/training-2/}{courses and workshops} \\
   2013 & RIKEN/KI doctoral course: Epigenomics: Methods and Applications to Disease and Development \\
   2012 & SISSA summer school on dopaminergic neurons \\
   2012 & RIKEN/KI doctoral course: Functional Regulation in Development and Disease \\
   2011 & UQ winter school in mathematical and computational biology \\
   2011 & RIKEN/EBI bioinformatics roadshow \\
\end{tabular}

\section*{Academic and Administrative Experience}
\begin{tabular}{L!{\VRule}R}
   2015 & MODHEP workshop presenter on \href{https://github.com/davetang/cage_r}{analysing CAGE data using R} \\
   2013--2014 & Organiser of the Chat with Guest sessions at RIKEN CLST DGT \\
   2013--2014 & Organiser of the Student Journal Club at RIKEN CLST DGT \\
   2013 & Organising committee for the \href{http://www.nature.com/natureevents/science/events/20919-BrainTrain_Conference}{BrainTrain conference} \\
   2013 & Organiser of the BrainTrain workshop: Identifying regulatory elements in the genome \\
\end{tabular}

\section*{Hobbies and Interests}

Sports (especially basketball), cycling, bioinformatics blogging, self study, and computer games.

\section*{Academic References}

\begin{minipage}[ht]{.50\textwidth}
Brian Dalrymple \\
Queensland Bioscience Precinct \\
306 Carmody Road \\
St Lucia QLD 4067 \\
Australia \\
\href{mailto:brian.dalrymple@csiro.au}{brian.dalrymple@csiro.au}
\end{minipage}
\begin{minipage}[ht]{.50\textwidth}
Piero Carninci \\
RIKEN Yokohama Campus \\
1-7-22 Suehiro-cho, Tsurumi-ku, Yokohama \\
Kanagawa 230-0045 \\
Japan \\
\href{mailto:carninci@riken.jp}{carninci@riken.jp}
\end{minipage}

\section*{Publications}
% http://tex.stackexchange.com/questions/22645/hiding-the-title-of-the-bibliography
\begingroup
   \renewcommand{\section}[2]{}%
   \bibliographystyle{unsrturl}
   \nocite{*}
   \bibliography{pub}
\endgroup

\vfill

\footnotesize
This C.V. was prepared in \LaTeX\ and is available at \href{https://github.com/davetang/cv}{https://github.com/davetang/cv}.

\end{document}
