---
title: "Making a CV with R"
author: "Dave Tang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install `vitae`

Install the `vitae` package, if you haven't already.

```{r install}
if(!"vitae" %in% installed.packages()){
  install.packages('vitae')
}
library(vitae)
```

## Creating a CV

See an [introduction to vitae](https://ropenscilabs.github.io/vitae/articles/vitae.html). Using RStudio, simply use the RStudio R Markdown template selector to create a new CV document. This is done by going to "File" -> "New File" -> "R Markdown" and then selecting "From Template".

## Scholar

The `awesome` template using the [scholar package](https://cran.r-project.org/web/packages/scholar/vignettes/scholar.html); this is handy if you have a Google Scholar page.

```{r install_scholar, message = FALSE, warning=FALSE}
if(!"scholar" %in% installed.packages()){
  install.packages('scholar')
}

library(scholar)
```

Get my Google Scholar profile.

```{r get_profile}
id <- '7uxzL2QAAAAJ'

l <- get_profile(id)

l
```

Get my publications.

```{r get_pubb}
p <- get_publications(id)

library(dplyr)
p %>%
  filter(cites > 0) %>%
  select(title, journal, year, cites) %>%
  DT::datatable()
```

Get my citation history.

```{r get_cit_hist}
ct <- get_citation_history(id)
ct
```
